Bow shocks, bow waves, and dust waves. I. Strong coupling limit

### 2019-04-08 papers/Papers1234/sec-obs-intro.tex
Write some introduction to Paper IV

@@

@@

@@

Cooler red supergiant and asymptotic giant branch stars
\citep{Ueta:2008a, Sahai:2010a, Cox:2012a}.

Instability of bow \citep{Blondin:1988a}

>>>>

Stellar bow shocks are produced by the relative motion between a star
and its surrounding medium, and are commonly detected as curved arcs
of emission at optical \citep{Gull:1979a, Brown:2005a}, infrared
\citep{van-Buren:1988a, Kobulnicky:2016a}, or radio
\citep{van-Buren:1990a, Benaglia:2010a} wavelengths.  The canonical
theory for these objects is that they are formed by a two-shock
interaction between the stellar wind and the interstellar medium
\citep{Pikelner:1968a, Dyson:1972a}, which is distorted due to the
supersonic motion of the star \citep{Baranov:1970a, Wilkin:1996a}.  In
some instances, however, the absorbed stellar radiation pressure may
be more important than the stellar wind in providing the inner support
for the bow shell \citep[Paper~I]{Henney:2019a} and this may even be
sufficient to break the collisional coupling between gas and dust
grains \citep[Paper~II]{Henney:2019b}.  In other cases, the appearance
of an infrared emission arc may be due to the illumination of the
inner wall of an asymmetrical cavity \citep{Mackey:2016a}, rather than
the formation of a dense shell, in which case the relative velocity of
the star may be subsonic with respect to its surroundings
\citep{Mackey:2015a}.

The largest number of bow shocks have been detected around OB stars,
via their mid-infrared dust emission \citep{van-Buren:1995a,
  Smith:2005a, Povich:2008a, Kobulnicky:2010a, Peri:2012a, Peri:2015a,
  Sexton:2015b, Kobulnicky:2016a, Bodensteiner:2018a}, and these have
sizes ranging from \SIrange{0.01}{1}{pc}.

@@

Interaction of wind with photoevaporation flow \citep{Dyson:1975a}

@@

Wolf-Rayet bow shock nebulae \citep{Dyson:1989a}

@@

Cooler red supergiant and asymptotic giant branch stars
\citep{Ueta:2008a, Sahai:2010a, Cox:2012a}. 
Bowshocks from red supergiants \citep{Meyer:2014a}

Instability of bow \citep{Blondin:1998a}

### 2019-04-08 papers/Papers1234/sec-observational-diagnostics.tex
Write some introduction to Paper IV

In Figure~\ref{fig:All-sources-eta-tau} we show the resultant
diagnostic diagram: \(\eta\shell\) versus \(\tau\).  The horizontal axis
shows the fraction of the stellar radiative \emph{energy} that is
reprocessed by the bow shell, while the vertical axis shows the
fraction of stellar radiative \emph{momentum} that is imparted to the
shell, either directly by absorption, or indirectly by the stellar
wind (which is itself radiatively driven).  Radiatively supported bows
(DW, RBW, or RBS, or cases) should lie on the diagonal line
\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where we have used
the ratio of grain radiation pressure efficiency to absorption
efficiency found in the FUV band for the dust mixture shown in
Paper~II's Figure~6.  Wind-supported bows should lie above this line
and no bows should lie below the \(\eta\shell = \tau\) line, since
\(Q_P\) cannot be smaller than \(Q_{\text{abs}}\).

@@

The small bow sizes are fully consistent with the expectations from
the theory developed in Paper~I.  Radiation-supported bows are predicted
to occur either in high-density environments
(\(n > \SI{100}{cm^{-3}}\)) or for stars with particularly weak winds.
In either case, the bow is expected to be smaller than \SI{0.1}{pc}
for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~6 of
Paper~I.\@

>>>>

In Figure~\ref{fig:All-sources-eta-tau} we show the resultant
diagnostic diagram: \(\eta\shell\) versus \(\tau\).  The horizontal axis
shows the fraction of the stellar radiative \emph{energy} that is
reprocessed by the bow shell, while the vertical axis shows the
fraction of stellar radiative \emph{momentum} that is imparted to the
shell, either directly by absorption, or indirectly by the stellar
wind (which is itself radiatively driven).  Radiatively supported bows
(DW, RBW, or RBS cases) should lie on the diagonal line
\(\eta\shell = ( Q_P / Q_{\text{abs}}) \tau \approx 1.25 \tau\), where we have used
the ratio of grain radiation pressure efficiency to absorption
efficiency found in the FUV band for the dust mixture shown in
Paper~II's Figure~6.  Wind-supported bows should lie above this line
and no bows should lie below the \(\eta\shell = \tau\) line, since
\(Q_P\) cannot be smaller than \(Q_{\text{abs}}\).

@@

The small bow sizes are fully consistent with the expectations from
the theory developed in Paper~I.  Radiation-supported bows are predicted
to occur either in high-density environments
(\(n > \SI{100}{cm^{-3}}\)) or for stars with particularly weak winds.
In either case, the bow is expected to be smaller than \SI{0.1}{pc}
for \(v_\infty \ge \SI{20}{km.s^{-1}}\), see Figures~2a,b and~8 of
Paper~I.\@
